### 2023-07-26 manuscript.tex
Updated data availability statement

\subsection{Code and data availability}
\begin{sloppypar}
The code used to produce the results and analyses is available at \url{https://github.com/marcsingleton/orthology_inference2023}. HMM algorithms were implemented in the standalone package Homomorph which is available at \url{https://github.com/marcsingleton/homomorph} and on the Python Package Index (PyPI). The following Python libraries were used: matplotlib~\cite{Hunter2007}, NumPy~\cite{Harris2020}, pandas~\cite{McKinney2010}, and SciPy~\cite{Virtanen2020}. Relevant output files are available in the supporting information. There are no primary data associated with this manuscript. All primary data are available from publicly accessible sources described in their corresponding sections.
\end{sloppypar}

>>>>

\subsection{Code and data availability}
\begin{sloppypar}
The code used to produce the results and analyses is available at \url{https://github.com/marcsingleton/orthology_inference2023}. HMM algorithms were implemented in the standalone package Homomorph which is available at \url{https://github.com/marcsingleton/homomorph} and on the Python Package Index (PyPI). The following Python libraries were used: matplotlib~\cite{Hunter2007}, NumPy~\cite{Harris2020}, pandas~\cite{McKinney2010}, and SciPy~\cite{Virtanen2020}. There are no primary data associated with this manuscript. All primary data are available from publicly accessible sources described in their corresponding sections. Relevant outputs are available in the supplemental files at FigShare. File S1 contains the orthologous groups generated by 4-clique percolation with paralogs added. File S2 contains the initial alignments of all sequences in each orthologous group. File S3 contains the refined alignments of the representative sequences in each single copy orthologous group. File S4 contains the insertion phylo-HMM model parameters and the alignments of the single copy ortholog groups after trimming. File S5 contains the missing data phylo-HMM model parameters and the missing segments identified for each sequence in each single copy orthologous group. Missing segments are given as Python slices in the following form: start0-stop0,start1-stop1,\ldots,startn-stopn. If the slices field is empty, then no missing segments were identified in that sequence. File S6 contains the consensus phylogenetic trees fit using the LG, GTR, and GTR2 substitution models.
\end{sloppypar}
